$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-04-10 paper/e6ssm-tuning-paper.tex
Corrected caption on chargino plot to match legend on plot

\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{mssm_chargino_plot_bw_var.png}}%%
\caption{Scatter plot of fine tuning vs lightest Higgs mass in the MSSM with
$m_{\tilde{\chi}^\pm_1} = 200$ GeV shown in light blue (bottom band),
$m_{\tilde{\chi}^\pm_1} = 500$ GeV in dark blue (middle band), and
$m_{\tilde{\chi}^\pm_1} = 700$ GeV in dark yellow (top band).}
\label{Fig:chargino-plot}
\end{center}
\end{figure}

>>>>

\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{mssm_chargino_plot_bw_var.png}}%%
\caption{Scatter plot of fine tuning vs lightest Higgs mass in the MSSM with
$200 \textrm{ GeV} \leq m_{\tilde{\chi}^\pm_1} \leq 400$ GeV shown in light
blue (bottom band), $500 \textrm{ GeV} \leq m_{\tilde{\chi}^\pm_1} \leq 600$
GeV in dark blue (middle band), and $700 \textrm { GeV} \leq
m_{\tilde{\chi}^\pm_1} \leq 800$ GeV in dark yellow (top band).}
\label{Fig:chargino-plot}
\end{center}
\end{figure}
